
---
title: "Homework_Data Visualization Batch 10"
author: "Phubordin Phanyosri"
date: "2025-01-04"
output:
  html_document: default
  pdf_document: default
---

\begin{center}
\textbf{\LARGE The First Thing To Do}
\end{center}

### Download Related library !!
```{r}
library(knitr)
library(tidyverse)
```
## 0) Given Sample Dataset And Set Customize Theme
```{r}
set.seed(42)
small_data <- diamonds %>% 
              sample_frac(0.2) # 20% of the total number of rows

```
```{r, warning = FALSE, message = FALSE}
custom_theme <- theme_linedraw() + # Use AI to help design ideas to customize 
                                   # the theme of the diagram. 
  theme(
    # Darker plot title
    plot.title = element_text(
      face = "bold",
      size = 16,
      color = "black",
      margin = margin(b = 10)
    ),
    # Darker subtitle
    plot.subtitle = element_text(
      size = 12,
      color = "#2F4F4F",  # Dark slate gray
      margin = margin(b = 15)
    ),
    # Darker caption
    plot.caption = element_text(
      size = 8,
      color = "#4A4A4A",  # Darker gray
      margin = margin(t = 10)
    ),
    # Darker axis titles
    axis.title = element_text(
      size = 11,
      color = "#1C1C1C",  # Very dark gray
      face = "bold"
    ),
    # Darker axis text
    axis.text = element_text(
      size = 9,
      color = "#2F4F4F"  # Dark slate gray
    ),
    # Customize facet labels
    strip.text = element_text(
      face = "bold",
      size = 10,
      color = "white"
    ),
    strip.background = element_rect(
      fill = "#2F4F4F",  # Dark slate gray
      color = "black"
    ),
    # Darker panel elements
    panel.grid.major = element_line(
      color = "#BEBEBE",  # Medium gray
      size = 0.3
    ),
    panel.grid.minor = element_line(
      color = "#D3D3D3",  # Light gray
      size = 0.2
    ),
    panel.border = element_rect(
      color = "black",
      size = 0.8
    ),
    # Add margin around the plot
    plot.margin = margin(15, 15, 15, 15),
    # Darker background
    panel.background = element_rect(
      fill = "white"
    )
  )
```

\newpage

## 1) Distribution of price groups of diamonds by Density, Table.
###     a. Table: Price Ranges of Diamonds
```{r, echo=FALSE, message=FALSE}

small_data %>%
  mutate( # Create a new column for diamond price ranges
    price_range = cut(
      price, breaks = seq(0, max(price), by = 500), 
      labels = paste(
        seq(0, max(price) - 500, by = 500), 
        seq(500, max(price), by = 500), sep = "-"
      )
    )
  ) %>%
  count(price_range) %>%
  head(10) %>% # Specify no more than 10 rows.
  kable(col.names = c("Price Range ($)", "Number of Diamonds"),
        caption = "Distribution of Diamond Prices by Range")
```
###     b. Density: Price Ranges of Diamonds
```{r, fig.align='center', fig.height = 3, fig.width = 5}
small_data %>%
  ggplot(aes(price)) +
  geom_density(fill = "#4682B4", alpha = 0.7) +
  custom_theme +
  theme(plot.background = element_rect(fill = "#f5e19f")) +
  labs(title = "Price Distribution of Diamonds", 
       subtitle = "The $500-$1000 price range has the largest number of diamonds.", 
       caption = "Source: ggplot Package", 
       x = "Diamond Price Range", 
       y = "Density")
```
\newpage

## 2) Sub-Diagram of Diamond Price Groups, Divided by cut.
```{r, fig.align='center'}
small_data %>%
  ggplot(aes(price)) +
  geom_density(fill = "#4682B4", alpha = 0.7) +  # Steelblue with higher opacity
  custom_theme +
  theme(plot.background = element_rect(fill = "#f5e19f")) +
  labs(title = "Price Distribution of Diamonds", 
       subtitle = "Sub-diagram of diamond price groups, divided by cut", 
       caption = "Source: ggplot Package", 
       x = "Diamond Price Range", 
       y = "Density") +
  facet_wrap(~ cut)
```
\newpage

## 4) Depth Distribution Across Diamond Cut Quality.
###     a. Boxplot: Comparing Depth Values for Cut Quality
```{r}
small_data %>%
  filter(depth > 60) %>% # Interested in the balance value of 
                          # the diamond shape of more than 60%
  ggplot(aes(cut, depth, fill = cut)) +
  geom_boxplot() +
  custom_theme +
  theme(plot.background = element_rect(fill = "#f5e19f")) + 
  labs(
    title = "Depth Distribution Across Diamond Cut Quality",
    subtitle = "Comparing Depth Values for 'Fair', 'Good', 'Very Good', 'Premium', 
                                            and 'Ideal' Cuts",
    caption = "Source: ggplot2 Diamonds Dataset",
    x = "Cut Quality",
    y = "Depth Percentage (%)"
  )
```

\newpage

###     b. Scatter: Dist. of Diamond Shapes with Prices by Diamond Color
```{r}
small_data %>%
  filter(depth > 50) %>%
  ggplot(aes(depth, price, color = color)) +
  geom_point() +
  facet_wrap(~ cut) +
  custom_theme +
  theme(plot.background = element_rect(fill = "#f5e19f")) + 
  labs(
    title = "Dist. of Diamond Shapes with Prices by Diamond Color",
    subtitle = "Provided by Cut Quality",
    caption = "Source: ggplot2 Diamonds Dataset",
    x = "Depth Percentage (%)",
    y = "Price ($USD)"
  )

```

\newpage

## 5) Correlation Between Carat and Diamond Price.
```{r}
small_data %>%
  filter(
    clarity %in% c("VS1", "VVS2", "VVS1", "IF"), 
    color %in% c("G", "E", "F"), 
    cut %in% c("Ideal", "Premium", "Very Good")
  ) %>%
  ggplot(aes(carat, price, col = clarity)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, col = "red") +
  facet_grid(color ~ cut) + 
  custom_theme +
  theme(plot.background = element_rect(fill = "#f5e19f")) +
  labs(
    title = "Correlation Between Carat and Diamond Price",
    subtitle = "The overall correlation coefficient is 0.9215913.",
    caption = "Source: ggplot2 Diamonds Dataset",
    x = "Weigth (Carats)",
    y = "Price ($USD)"
  )

```


